04_DESeq_sexes

### 2019-07-19 analysis/04_DESeq2_sexes.Rmd
pause manip
now with manipulation bar graphs

library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)
library(forcats)

@@

```{r characterization}
g <- plotserialDEGs(DEGs.female_hypothalamus, "Female hypothalamus", "#00A08A")
h <- plotserialDEGs(DEGs.female_pituitary, "Female pituitary", "#00A08A")
i <- plotserialDEGs(DEGs.female_gonad, "Female gonad", "#00A08A")
j <- plotserialDEGs(DEGs.male_hypothalamus, "Male hypothalamus", "#F98400")
k <- plotserialDEGs(DEGs.male_pituitary, "Male pituitary", "#F98400")
l <- plotserialDEGs(DEGs.male_gondad, "Male gonad", "#F98400")

@@

pdf("../figures/sexes/characterization-1.pdf", width = 10, height = 6)
plot(mybarplots)
dev.off()
```

```{r manipulation}

>>>>

library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)
library(forcats)
library("wesanderson")

@@

```{r characterization}
# bars with lines
g <- plotserialDEGs(DEGs.female_hypothalamus, "Female hypothalamus", "#00A08A")
h <- plotserialDEGs(DEGs.female_pituitary, "Female pituitary", "#00A08A")
i <- plotserialDEGs(DEGs.female_gonad, "Female gonad", "#00A08A")
j <- plotserialDEGs(DEGs.male_hypothalamus, "Male hypothalamus", "#F98400")
k <- plotserialDEGs(DEGs.male_pituitary, "Male pituitary", "#F98400")
l <- plotserialDEGs(DEGs.male_gondad, "Male gonad", "#F98400")

@@

pdf("../figures/sexes/characterization-1.pdf", width = 10, height = 6)
plot(mybarplots)
dev.off()

# lines only, different colors for different sex tissue groups
FH <- subsetDEGs(DEGs.female_hypothalamus, "Female hypothalamus")
FP <- subsetDEGs(DEGs.female_pituitary, "Female pituitary")
FG <- subsetDEGs(DEGs.female_gonad, "Female gonad")
MH <- subsetDEGs(DEGs.male_hypothalamus, "Male hypothalamus")
MP <- subsetDEGs(DEGs.male_pituitary, "Male pituitary")
MG <- subsetDEGs(DEGs.male_gondad, "Male gonad")

specificDEGs <- rbind(FH, FP, FG, MH, MP, MG)

specificDEGs$sextissue <- factor(specificDEGs$sextissue, levels = c("Female hypothalamus", "Female pituitary", "Female gonad",
                                                                    "Male hypothalamus", "Male pituitary", "Male gonad"))
mylinegraph <- ggplot(specificDEGs, aes(x=comparison, y=V3, group = sextissue)) +
    geom_line(aes(color=sextissue)) +
    geom_point(aes(color=sextissue)) + 
    theme_minimal(base_size = 10) +
    #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "Parental stage transitions", y= "No. of differentially expressed genes ",
         title = "Gene expression changes during parental care transitions") + 
    scale_x_discrete(labels=c("Control to\nNest bldg", "Nest bldg. to\nLay", "Lay to\nInc. day 3",
                              "Inc. day 3 to\nInc. day 9", "Inc. day 9 to\nInc. day 17",
                              "Inc. day 17 to\nHatch", "Hatch to\nNestling day 5", "Nestling day 5 to\n Nestling day 9")) +
   theme(legend.title = element_blank(),
         legend.position = c(0.8, 0.8))

mylinegraph

pdf("../figures/sexes/characterization-2.pdf", width = 8, height = 4)
plot(mylinegraph)
dev.off()
```

```{r manipVchar}
g <- plotmanipDEGs(DEGs.female_hypothalamus, "Female hypothalamus", "bottom")
h <- plotmanipDEGs(DEGs.female_pituitary, "Female pituitary", "none")
i <- plotmanipDEGs(DEGs.female_gonad, "Female gonad",  "none")
j <- plotmanipDEGs(DEGs.male_hypothalamus, "Male hypothalamus", "none")
k <- plotmanipDEGs(DEGs.male_pituitary, "Male pituitary", "none")
l <- plotmanipDEGs(DEGs.male_gondad, "Male gonad", "none")

legend <- get_legend(g)

mybarplots <- plot_grid(g + theme(legend.position = "none"), h , i , j ,k , l, nrow = 2)

mybarplots2 <- plot_grid(mybarplots, legend, ncol = 1, rel_heights = c(1,0.1))
mybarplots2

pdf("../figures/sexes/manipVchar-1.pdf", width = 10, height = 6)
plot(mybarplots2)
dev.off()

plotmanipDEGs(DEGs.male_pituitary, "Male pituitary", "bottom")
```
